Tables

### 2018-03-29 code/tables.rmd
Paper version of heterogeneity table

#this function is for transforming RRR8 which only has raw mean difference and SE to a standardized version
transform_SE <- function(ES, SE, n1, n2){ #Based on meta-analysis lecture 02
  sdpooled <- sqrt(SE^2 / (1 / n1 + 1/n2))
  d <- ES / sdpooled
  g <- (1 - 3 / (4*(n1 + n2) - 9))*d
  v <- 1 / n1 + 1/ n2 + g^2 / (2*(n1 + n2))
  data.frame(g = g, v = v)
}

est_heterogen_smd_raw <- function(x){
  if(any(x[, "outcomes1_2"] == "mean _ SD")){ #without the 'any' we will get warnings because we apply 'if' to a vector

    fit <- rma(measure = "SMD", m1i = outcome_t1, m2i = outcome_c1, sd1i = outcome_t2, sd2i = outcome_c2, #gives Hedge's g as outcome
               n1i = ntreatment, n2i = ncontrol,test = "knha", data = x)

    fit2 <- rma(measure = "MD", m1i = outcome_t1, m2i = outcome_c1, sd1i = outcome_t2, sd2i = outcome_c2, #gives raw outcome
               n1i = ntreatment, n2i = ncontrol,test = "knha", data = x)

@@

    standardized <- transform_SE(x$effect_size, x$outcome_c2, x$ntreatment, x$ncontrol)

    fit <- rma(yi = g, vi = v, test = "knha", data = standardized) #standardized effect estimate

    fit2 <-  rma(yi = effect_size, sei = outcome_c2, test = "knha",  data = x) #raw effect estimate

@@

    fit <- fit2 <- rma(measure = "COR", ri = effect_size, ni = Ntotal, test = "knha", data = x) #raw correlation

    I2_1 <- confint(fit)$random[3, ] #Gives us the I2 estimate and its confidence interval for standardized values
    I2_2 <- rep(NA, 3) #No unstandardized version

    return(data.frame(eff_size = fit$b[[1]],
                      s_I2 = I2_1[1], s_ci.lb = I2_1[2], s_ci.ub = I2_1[3], 
                      r_I2 = I2_2[1], r_ci.lb = I2_2[2], r_ci.ub = I2_2[3]))

@@

    fit <- rma(measure = "OR2DL", ai = outcome_t1, bi = outcome_t2, ci = outcome_c1, di = outcome_c2, #standardized, ML1 used 'OR2D' but this = 'OR2DL'
               n1i = ntreatment, n2i = ncontrol, test = "knha", data = x)

    fit2 <- rma(measure = "RD", ai = outcome_t1, bi = outcome_t2, ci = outcome_c1, di = outcome_c2, #unstandardized
               n1i = ntreatment, n2i = ncontrol, test = "knha", data = x)
  }

  I2_1 <- confint(fit)$random[3, ] #Gives us the I2 estimate and its confidence interval for standardized values
  I2_2 <- confint(fit2)$random[3, ] #Gives us the I2 estimate and CI for raw values

  data.frame(eff_size = fit$b[[1]], #standardized effect (point estimate)
             s_I2 = I2_1[1], s_ci.lb = I2_1[2], s_ci.ub = I2_1[3], #standardized I2 + CI
             r_I2 = I2_2[1], r_ci.lb = I2_2[2], r_ci.ub = I2_2[3]) #unstandardized I2 + CI
}

#Apply function to data
res <- dat %>% 
  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
  map_dfr(est_heterogen_smd_raw, .id = "effect") %>% #apply function, rbind results into dataframe ('dfr'), make sure purrr is up to date
  mutate(dif = s_I2 - r_I2) #Gives us the difference between the two

clarify <- c("Allowed vs. forbidden", "Gain vs. loss framing", "Norm of reciprocity", "Low vs. high category scales") #Effects reported as d in many labs 1 but meta-analyzed as OR

#Add rs to the data-frame
het <- dat %>% 
  select(rs, effect, effect_type) %>% 
  group_by(rs, effect) %>% 
  summarize(effect_type = unique(effect_type)) %>% 
  left_join(res) %>% 
  mutate(effect_type = recode(effect_type, 
                              d = "Mean diff.",
                              r = "Correlation",
                              'Raw mean difference' = "Mean diff.",
                              'Risk difference' = "OR / RD"),
         effect_type = ifelse(effect %in% clarify, "OR / RD", effect_type)) %>% 
  arrange(desc(s_I2)) #sort by I2 for standardized effect
```

##Heterogeneity in preregistered multi-lab psychology studies
```{r heterogeneity-table}
library(kableExtra)
het %>% knitr::kable("latex", booktabs = T, digits = 1, col.names = c("RS", "Effect", "Effect type", "Estimate", "I2(%)", "ci.lb", "ci.ub", "I2(%)", "ci.lb", "ci.ub", "Dif")) %>% 
  kable_styling(latex_options = "scale_down") %>% 
  add_header_above(c(" " = 4, "Standardized" = 3, "Unstandardized" = 3, " " = 1)) %>%
  footnote(threeparttable = TRUE,
           general = "'OR / RD' indicates that the effect was meta-analyzed as odds ratio in 'standardized' columns and risk difference in 'unstandardized' columns. Out of these effects 'Verbal overshadowing' was meta-analyzed by original authors as risk difference and the others as odds ratios. For correlations the standardized version correspond to raw correlations.  For 'Mean diff.' the standardized version corresponds to Hedge's g and unstandardized to raw mean differences. Original authors used different approaches for mean differences. RRR5 I have not yet been able to extract a measure of variance for, hence the NAs. Effects were estimated in metafor using REML with the 'knha' correction. Estimate column are point estimates of standardized effect sizes.")

>>>>

est_heterogen_smd_raw <- function(x){
  if(any(x[, "effect_type"] == "Risk difference")){ #without the 'any' we will get warnings because we apply 'if' to a vector

    fit <- rma(measure = "RD", ai = outcome_t1, bi = outcome_t2, ci = outcome_c1, di = outcome_c2,  n1i = ntreatment, n2i = ncontrol, test = "knha", data = x)

@@

    fit <-  rma(yi = effect_size, sei = outcome_c2, test = "knha",  data = x)

  } else if(any(x[, "effect_type"] == "Raw mean difference")){

    fit <- rma(measure = "MD", m1i = outcome_t1, m2i = outcome_c1, sd1i = outcome_t2, sd2i = outcome_c2, n1i = ntreatment, n2i = ncontrol,test = "knha", data = x)

  } else if(any(x[, "outcomes1_2"] == "mean _ SD")){

    fit <- rma(measure = "SMD", m1i = outcome_t1, m2i = outcome_c1, sd1i = outcome_t2, sd2i = outcome_c2, n1i = ntreatment, n2i = ncontrol,test = "knha", data = x)

@@

    fit <- rma(measure = "COR", ri = effect_size, ni = Ntotal, test = "knha", data = x)

@@

    fit <- rma(measure = "OR2DL", ai = outcome_t1, bi = outcome_t2, ci = outcome_c1, di = outcome_c2, #standardized, ML1 used 'OR2D' but that = 'OR2DL'
               n1i = ntreatment, n2i = ncontrol, test = "knha", data = x)

  }

  I2_1 <- confint(fit)$random[3, ] #Gives us the I2 estimate and its confidence interval
  data.frame(eff_size = fit$b[[1]], #effect size (point estimate)
             p = fit$pval,
             s_I2 = I2_1[1], s_ci.lb = I2_1[2], s_ci.ub = I2_1[3]) #I2 + CI
}

#Apply function to data
res <- dat %>% 
  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
  map_dfr(est_heterogen_smd_raw, .id = "effect") #apply function, rbind results into dataframe ('dfr'), make sure purrr is up to date

OR <- c("Allowed vs. forbidden", "Gain vs. loss framing", "Norm of reciprocity", "Low vs. high category scales") #Effects reported as d in many labs 1 but meta-analyzed as OR

#Add rs to the data-frame
het <- dat %>% 
  select(rs, effect, effect_type) %>% 
  group_by(rs, effect) %>% 
  summarize(effect_type = unique(effect_type)) %>% 
  left_join(res) %>% 
  mutate(effect_type = recode(effect_type, 
                              d = "Std. mean diff.",
                              r = "Correlation",
                              'Raw mean difference' = "Raw mean diff.")) %>% 
  arrange(desc(s_I2)) #sort by I2 for standardized effect
```

##Heterogeneity in preregistered multi-lab psychology studies
```{r heterogeneity-table}
library(kableExtra)
het %>% knitr::kable("latex", booktabs = T, digits = 2, col.names = c("RS", "Effect", "Effect type", "Estimate", "p-value", "I2(%)", "ci.lb", "ci.ub")) %>% 
  kable_styling() %>%
  footnote(threeparttable = TRUE,
           general = "We meta-analyzed effects using the same outcome measures that were used by the original authors. Standardized mean difference is Hedge's g. The following effects are odds ratios transformed into standardized mean differences: 'Allowed vs. forbidden', 'Gain vs. loss framing', 'Norm of reciprocity', 'Low vs. high category scales'. Effects were estimated in metafor using REML with the 'knha' correction. Estimate column are point estimates of effect sizes. Final columns are the upper and lower boundaries of the 90% confidence interval for I2.")
